---
title: "lab-07-simpsons.Rmd"
author: Fawzaih Nazal
date: 17 March 2021
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}
Whickham
```
    
Your answer: The data is observational as the description states that is based on age, smoking, and mortality, which are all observable events and not produced via experiments

2.  
```{r observations}
nrow( Whickham)
```

Your answer;There 1,314 observations.As we know every row is an observation ,age ,smoker,outcome.

3.  

```{r number_variables}
names(Whickham)
```

Your answer:There are 3 variables , "outcome" , "smoker" , and "age"  

```{r var_type}
unique(Whickham$outcome)
unique(Whickham$smoker)
unique(Whickham$age)
```

Your answer: Using the unique() function on the 3 variables we could see that "outcome" only takes Alive or Dead  value , which makes it categorical non-ordinal. "smoker"only takes yes or No , which also makes it categorical non-ordinal.Age is numerical continous data. 

One of the best ways to visualise categorical data is through the use of bar charts.


```{r plot_outcome}
ggplot(Whickham, aes(x = outcome)) +

 geom_bar()
```


```{r plot_smoker}
ggplot(Whickham, aes(x = smoker)) +
 geom_bar()
```

```{r plot_age}
 ggplot(Whickham, aes(x = age)) +
 geom_bar()
```


4. 
NA: I expect that the more and continuing to smoke will destroy health and increase diseases and make the health condition worse .

```{r plot_smokeVSincome_1}
ggplot(data=Whickham, aes(x=smoker, y=outcome, color=outcome)) + geom_bar(stat="identity")
```
Knit, commit, and push to github.

5. 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
```

6.

```{r age_cat}

```

7. 

```{r plot_smokeVSincome_3}

```

Knit, commit, and push to github.